### 2015-05-05 Workshop2015/camera-ready/computingDerivSLA.tex
version à 6 pages

The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedS LAs of potential composable services. This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.

@@

In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
\begin{trivlist}\sf\footnotesize
 \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
 \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
 \item[~-~freshness:] non.
 \item[~-~provenance:] all services involved must be $expert$.
 \item[~-~duration:] 7 days.
 \item[~-~I/0 volume/month:] 8GB.
 \item[~-~reputation level :] $\geq$ threshold.
 \item[~-~storageSpace:] 1GB.
 \end{trivlist}

>>>>

The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLA of potentially composable services. 
This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.

@@

In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
\begin{trivlist}\sf\footnotesize
 \item[~-~ total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1;
 \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$};
 ~-~freshness: non;
 \item[~-~provenance:] all services involved must be $expert$;
  ~-~duration: 7 days;
 \item[~-~I/0 volume/month:] 8GB;
  ~-~reputation level: $\geq$ threshold;
 \item[~-~storageSpace:] 1GB.
 \end{trivlist}

### 2015-05-05 Workshop2015/camera-ready/derivingSLA.tex
version à 6 pages

%-----------------------------------------------------------------
%\section{Deriving an Integration SLA: first approach}
%\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
 Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of the clouds involved.  This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be used in a query evaluation process. It is thus important to optimize the use of these resources.

The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.  Indeed, queries requesting the same service compositions will have clauses that are  conditions of use of the infrastructure (i.e., not storing the data produced by a service). Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it for other queries. 
Second, pre-computed queries and partial results can be also stored in cache or in a persistent support. Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries. Storing or not such SLAs  depends on the cloud subscription of the user that issued the query (data access, intermediate storage capacity, cost of storage, etc.).

Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints. In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process. Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself. This leads to the build of the \textit{integration SLA}.

>>>>

%-----------------------------------------------------------------
%\section{Deriving an Integration SLA: first approach}
%\label{sec:queryProcessOpt}
%-----------------------------------------------------------------
 Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of those clouds.  
The use of resources from a cloud is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources used for query evaluation. 
It is thus important to optimize the use of these resources.

The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.  
Indeed, queries requesting the same service compositions may have clauses that are conditions of use of the infrastructure (i.e., not storing the data produced by a service). 
Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it in future queries. 
Second, pre-computed queries and partial results can be also stored in cache or in a persistent support. %Rewriting results can be stored and reduce execution and resources consumption time when evaluating similar queries. 
Storing or not these results depends on the cloud subscription SLA of the user (data access, intermediate storage capacity, storage cost, etc.).

%Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account  integration constraints. In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process. 
%Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself. Finally, query time execution will be stored  for further partial or similar queries.
%This leads to the build of the \textit{integration SLA}.

### 2015-05-05 Workshop2015/camera-ready/incremental.tex
version à 6 pages

To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
%starting from the processing of the query  to the delivery of the results.
Figure~\ref{fig:arch}). In this section, we present  step-by-step data integration process with the implied  SLA categories.

@@

Consumers will express queries  expressed as  Datalog-like programs or  SQL-like expressions, including spatio-temporal attributes and preferences.
For instance, the following query $Q_1$ ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.

The abstract Inter-Cloud Layer (ICL) delivers the results to the  query. The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry (SCS).

Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
We represent these providers respectively by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs  have the same interface as individual service providers.
We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates. 
All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements associated to the query.

@@

\begin{figure*}
\center{
\includegraphics[width=0.75\textwidth]{workflow.pdf}
\caption{SLA guided  data integration workflow.\label{fig:arch}}}
\end{figure*}

@@

Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).  Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment. It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

In our scenario, examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
The cost is determined by the  cost of the calls. 
This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for. The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.

As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ... e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which export  an API, composed of the following set of methods:

@@

In this paper, we are interested in the process of rewriting queries  considering QoS user preferences and SLAs.
This process includes the following phases: 
\begin{enumerate}
\item  User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} are  used to produce a \textit{derived SLA} to be associated to the query. The {\em derived SLA}  influences the choice of (data) services that will actually be used for building the result; 
\item Computing service compositions that rewrite the initial query and that can be used for  building query results. The \textit{agreed SLA} exported by the chosen services is added as  conditions in  each re-written query expression. 
Rewritten queries expressed as service composition can fully or partially comply with the \textit{derived SLA}.  An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration; 
\item   Managing the integration process according to the \textit{integration SLA}.
\end{enumerate}

>>>>

To answer this question, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
Figure~\ref{fig:arch}). 
We present a step-by-step data integration process and the implied  SLA categories.

@@

Consumers will specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
For instance, the following query $Q_1$: ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and are labeled as experts, where the total cost is less than 1 dollar, using only services that preserve their anonymity}''.

The Abstract Inter-Cloud Layer (ICL) delivers the results to the  query. 
The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry.

Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
We represent these providers respectively by { e$_1$ - e$_4$}, {h$_1$}, {h$_2$}. 
We suppose that hubs  have the same interface as individual service providers.
We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position.
All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements of the query.

@@

\begin{figure*}
\center{
\includegraphics[width=0.65\textwidth]{workflow.pdf}
\caption{SLA guided  data integration workflow.\label{fig:arch}}}
\end{figure*}

@@

Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).  Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment. It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
An \textit{agreed SLA} is given as an  XML document using the specification WSLA (Web service level agreement\footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).

In our scenario, an example of computed measure is the cost of retrieving ``expert'' Emily Dickinson poems providers within a region, with their cost. 
The cost is determined by the  cost of the calls. 
This request  includes the price of calling a service (e.g.,  between \$0,25 - 0,50, depending on the data service), plus the price of data transmission (amount of transmitted MB through the network), the type of subscription of the user for using the network and also the cost of applying encryption algorithms if required. 
The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.

As aforementioned, an \textit{a-priori} SLA enforcement mechanism is mandatory to assess data integration feasibility.
To this end, non-functional characteristics of the content provision services ({i.e e$_1$-e$_4$}) are calculated by specific cloud services that enforce SLA and which should export  an API, composed of the following methods:

@@

In this paper, we are interested in the process of rewriting queries  considering QoS user preferences and SLAs.
This process includes the following phases: 
\begin{trivlist}
\item[~1)]  User preferences (including cloud SLA according to user subscriptions) and \textit{agreed SLA} are  used to produce a \textit{derived SLA} to be associated to the query. 
{\em Derived SLA}  influences the choice of services that will be used to build the result; 
\item[~2)] Computing service compositions that rewrite the initial query and that are used to  build query results. 
The \textit{agreed SLA} exported by the chosen services is added as conditions in  each re-written query expression. 
Rewritten queries expressed as service composition can fully or partially comply with the \textit{derived SLA}.  An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration; 
\item[~3)]   Integration process guided by the \textit{integration SLA}.
\end{trivlist}

### 2015-05-05 Workshop2015/camera-ready/introduction.tex
version à 6 pages

\color{black}
The advent of cloud computing has imposed a new   resource consuming model that focusses on
 the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources. Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, and filtering them considering their "structural" characteristics (data variety that implies different formats and data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques have to be revisited considering weakly curated and modeled data sets. This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing  associated processing and integration processes.
In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. 
We believe in the benefits of SLA-based data integration as an approach for better meeting  user  requirements related to the conditions in which data is delivered and integrated, and on the quality of the data provided by services.
To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific  needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties for data (trust, privacy, reliability, etc).

@@

  From this scenario we identify a set of issues that have to be addressed. First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?  The user knows the low-level clauses of her SLA contract but she does not have an idea about the resources required to satisfy her requirements (SLA exported by services, example of Constraint 1).  Second, data services contracts should not be neglected in an integration process (Constraint 2).   As data services are deployed in a multi-cloud context, there is a need to establish the rules to determine how integration can be done and in which conditions. Intuitively, integration can be  done enforcing all specified conditions; but it is also possible to  expect situations where conditions can only be verified partially. Furthermore,  matching data providers with requests and QoS preferences with SLA's can be computationally costly. For this reason  the results of  such a  complex process  should be capitalized for further integration requests. How can this be done? The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a result for a given query.

We have proposed such architecture in \cite{BennaniGMV14}. With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneities among clouds. Furthermore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing particularly on query rewriting addressing security issues. We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user demands) that can contribute for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
%  Particularly, for queries that call several services deployed  on different clouds. 
%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration. How can the specified services requirements be enforced? And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.

Accordingly, the remainder of this paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments. Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process. Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.  Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach.

>>>>

\color{black}
The advent of cloud computing has imposed a new   resource consuming model that focuses on
 the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources. Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, and filtering them considering their "structural" characteristics (data variety that implies different formats and data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques have to be revisited considering weakly curated and modeled data sets. This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing  associated processing and integration processes.
In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. 
We believe in the benefits of SLA-based data integration as an approach for better meeting  user  requirements related to the conditions in which data is delivered and integrated, and on the quality of the data provided by services.
To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific  needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties for data (trust, privacy, reliability, etc).

@@

  From this scenario we identify a set of issues that have to be addressed. First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?  The user knows the low-level clauses of her SLA contract but she does not have an idea about the resources required to satisfy her requirements (SLA exported by services, example of Constraint 1).  Second, data services contracts should not be neglected in an integration process (Constraint 2).   As data services are deployed in a multi-cloud context, there is a need to establish the rules to determine how integration can be done and in which conditions. Intuitively, integration can be  done enforcing all specified conditions; but it is also possible to  expect situations where conditions can only be verified partially. Furthermore,  matching data providers with requests and QoS preferences with SLA's can be computationally costly. For this reason  the results of  such a  complex process  should be capitalized for further integration requests. How can this be done? The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a given query.

We have proposed such architecture in~\cite{BennaniGMV14}. With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneity among clouds. Furthermore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing particularly on query rewriting addressing security issues. We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.  Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services. The derived SLA allows to choose  services (w.r.t user demands) that can contribute for answering a query. Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
%  Particularly, for queries that call several services deployed  on different clouds. 
%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration. How can the specified services requirements be enforced? And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.

This paper is organized as follows. Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments. Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process. Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.  Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach.

### 2015-05-05 Workshop2015/camera-ready/queryRewriting.tex
version à 6 pages

Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
%Query rewriting is guided by the schema of  abstract and concrete databases.
The answers to the lower level queries are combined in order to obtain the result for the higher-level query.
The query rewriting problem can be generalized to the case of services.
In this case, the query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.

In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
%In the LAV approach, 
The rewriting process is guided by the specification of both the query to be rewritten and the available services.
%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
The solutions proposed are ranked and may be coded into concrete workflows as shown in the following sections.  
The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.

\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the MOOC scenario, where people can participate on a content trading pool.
We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.

When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
Depending on the location of the consumer and producers, different conditions and constraints may apply.
Also  cloud providers  publish the conditions for using their services.
These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.

In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.

In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition. The specification of each available service is also considered. 
%~\hfill\openbox
\end{example}

@@

The {\em agreed SLA} is included and merged with other SLA conditions that may be obtained by the rewriting process. Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.

In the case of our query example the following composition can be used for answering it:

\begin{footnotesize}
\sf
\begin{tabbing}
 -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
 \>  myLoc = loc(myIPaddress), \\
 \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
 \>  query total cost + cost $\leq$ \$1,\\
 \>  availability $\geq$ 90$\%$, \\
 \>  freshness = any, \\
 \>  provenance = ``expert'', \\
 \>  duration = 7 days, \\
 \>  I/0 volume/month $\leq$ 8GB, \\
 \>  reputation level $\geq \lambda$ (the threshold) \\
 \>  storageSpace $\leq$ 1GB, \\
 \>  engage(``E.Dickinson'', size, myCreditCard).
 \end{tabbing} 
\end{footnotesize}

>>>>

Query rewriting is a well-known problem for databases.
It consists in transforming an abstract query into lower-level queries that can be answered by available databases.
%Query rewriting is guided by the schema of  abstract and concrete databases.
The answers to the lower level queries are combined in order to obtain the result.
The query rewriting problem can be generalized to the case of services:
The query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
The latter case (\textit{i.e}, services that maintain and update information) is a generalization of the data provision case.
The general case requires considering the functional and non-functional aspects of the query and available services.
%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
%In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
%The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
%In the LAV approach, 
The rewriting process is guided by the specification of both the query to be rewritten and the available services.
%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
The solutions proposed are ranked and may be coded into concrete workflows.

The approach proposed in~\cite{CostaAMR13} which may be extended to the case of SLA-guided service-based data integration. 
%
%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
Let us consider the MOOC scenario, where people can participate on a content trading pool.
We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.

When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed.
%, in order to fetch each individual or hub service and to start  content retrieval procedures.
Depending on the location of the consumer and producers, different conditions and constraints may apply.
%Also  cloud providers  publish the conditions for using their services.
These conditions (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}.
In this context, the user  expresses a content order, her location and payment information. 
A composite  service is  generated to fulfill the order.
The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.

%In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition. The specification of each available service is also considered. 
%%~\hfill\openbox
%\end{example}

@@

The {\em agreed SLA} is included and merged with other SLA conditions that may be obtained by the rewriting process. Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
In the case of our query example the following composition can be used for answering it:

\begin{footnotesize}
\sf
\begin{tabbing}
 -~Q\=(myIPaddress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
 \>  myLoc = loc(myIPaddress), \\
 \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
 \>  query total cost + cost $\leq$ \$1, 
 \   availability $\geq$ 90$\%$, 
 \  freshness = any, \\
 \>  provenance = ``expert'', 
 \   duration = 7 days, 
 \   storageSpace $\leq$ 1GB, \\
 \>  I/0 volume/month $\leq$ 8GB, 
 \   reputation level $\geq \lambda$ (the threshold) \\
 \>  engage(``E.Dickinson'', size, myCreditCard).
 \end{tabbing} 
\end{footnotesize}
